Part II

### 2021-06-02 PartII.tex
updating by O

Given a homotopical trivialization of the action of $SO(d)$, then $\cA^q$ is a framed $E_d$ algebra.
More generally, given a map of Lie groups $G \to SO(d)$ and a compatible $G$-action on the theory, a homotopical trivialization of this action on the quantum theory equips $\cA^q$ with the structure of a $G$-framed $E_d$ algebra.
\end{thm}

@@

\begin{thm}
Given a homotopically $SO(d)$-trivial quantization of a classical AKSZ theory on $\RR^d$, 
factorization homology of the quantum observables 
\[
\int_{-} \cA^q : {\rm Bord}^{or}_d \to {\rm Alg}^{or}_d
\]
determines a fully extended oriented $d$-dimensional field theory with values in a higher Morita $(\infty,d)$-category of framed $E_d$ algebras.
\end{thm}

\owen{I should double-check whether Claudia or someone else has described this oriented Morita category ...}

\subsection{Chiral conformal field theories and vertex algebras}

\owen{I want to discuss how VOAs relate to factorization algebras, notably our CDO project, Si's results, and Brueggeman's thesis. We should also gesture at the Beilinson-Drinfeld approach.}

>>>>

Given a homotopical trivialization of the action of $SO(d)$, then $\cA^q$ is a framed $E_d$ algebra.
\end{thm}

More generally, given a map of Lie groups $G \to O(d)$ and a compatible $G$-action on the theory, a homotopical trivialization of this action on the quantum theory equips $\cA^q$ with the structure of a $G$-framed $E_d$ algebra.

@@

\begin{thm}
Given a homotopically $SO(d)$-trivial quantization of a classical AKSZ theory on $\RR^d$, 
factorization homology of the quantum observables 
\[
\int_{-} \cA^q : {\rm Bord}^{or}_d \to {\rm Alg}_d
\]
determines a fully extended oriented $d$-dimensional field theory with values in a higher Morita $(\infty,d)$-category of $E_d$ algebras.
\end{thm}

A similar claim applies to the general case with a map $G \to O(d)$.
